Copyright

### 2025-01-27 code.qmd
Add full license texts
Add DOI Citation Formatter
...and move CiteAs as it is not about
attributions, but citations.

Again, if the license required adding the full license text, you would also need to copy it to `LICENSE.txt` (if not already in there).
:::

@@

Now, add references for the software you would like to cite to the manuscript. In the following, we will demonstrate this for R and all R packages by using the R package `grateful`. For arbitrary software, you can use the [CiteAs service](https://citeas.org/) to create appropriate citations.

>>>>

Again, if the license required adding the full license text, you would also need to copy it to the project folder (if not already in there).
:::

@@

Now, add references for the software you would like to cite to the manuscript. In the following, we will demonstrate this for R and all R packages by using the R package `grateful`. For arbitrary software, you can use [CiteAs](https://citeas.org/) or the [DOI Citation Formatter](https://citation.doi.org/) to create appropriate citations.

### 2025-01-27 copyright.qmd
Add DOI Citation Formatter
...and move CiteAs as it is not about
attributions, but citations.

To determine whether a particular work can be included in the project folder and shared publicly, the first step is to search for its license. For example, this tutorial has an [about page](about.qmd) detailing its licensing, whereas other websites sometimes state the license in the footer. Other places to look include a project's `README` file or a dedicated `LICENSE` or `COPYING` file. If a project has been stored in a research repository, yet another means of communicating its copyright status might exist. For some repositories, external attribution generators exist:

- Wikimedia Commons: [Attribution Generator](https://lizenzhinweisgenerator.de/?lang=en)
- Various software repositories: [CiteAs](https://citeas.org/)

>>>>

To determine whether a particular work can be included in the project folder and shared publicly, the first step is to search for its license. For example, this tutorial has an [about page](about.qmd) detailing its licensing, whereas other websites sometimes state the license in the footer. Other places to look include a project's `README` file or a dedicated `LICENSE` or `COPYING` file. If a project has been stored in a research repository, yet another means of communicating its copyright status might exist. For media from Wikimedia Commons, an [Attribution Generator](https://lizenzhinweisgenerator.de/?lang=en) exists.
